\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-10-02 Manuscript/Manuscript.tex
PUB

\begin{table}[]
\caption{Performances of decision tree algorithm for the exoplanets habitability as evaluated by the accuracy, the no-information rate (NIR), and the $\phi$ factor.}
\begin{center}
\begin{tabular}{l|l}
\multicolumn{1}{c|}{Feature} & Value \\ \hline
\multicolumn{1}{c|}{Accuracy} & 0.978 \\ \hline
\multicolumn{1}{c|}{NIR} & 0.901 \\ \hline
\multicolumn{1}{c|}{$\phi$} & 0.874 \\ 
\label{DecisionTree_perf_tab}
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\caption{Performances of random forest algorithm for the exoplanets habitability as evaluated by the accuracy, the no-information rate (NIR), and the $\phi$ factor.}
\begin{center}
\begin{tabular}{l|l}
\multicolumn{1}{c|}{Feature} & Value \\ \hline
\multicolumn{1}{c|}{Accuracy} & 0.981 \\ \hline
\multicolumn{1}{c|}{NIR} & 0.899 \\ \hline
\multicolumn{1}{c|}{$\phi$} & 0.894 \\ 
\label{Random Forest_perf_tab}
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[htp]
  \centering
\subfloat[]{\label{Decision_Tree_FINAL_CV}\includegraphics[width=0.6\textwidth]{Pic/Decision_Tree_FINAL_CV.png}}\\
\subfloat[]{\label{Decision_Tree_FINAL_CV}\includegraphics[width=0.6\textwidth]{Pic/Decision_Tree_FINAL_ROC.png}}
\caption{The performances of the decision tree algorithm on the habitability of exoplanets as given by the confusion matrix (upper panel) and ROC curve (lower panel) as obtained by a 10-fold cross validation. A predicted (P) habitable exoplanet is classified as 1 while a test (T) non-habitable exoplanet is classified as 0}
\label{Decision_tree_performances}
\end{figure}

>>>>

\begin{table}[]
\caption{Performances of decision tree algorithm for the exoplanets habitability as evaluated by the accuracy, the no-information rate (NIR), and the $\phi$ factor.}
\begin{center}
\begin{tabular}{l|l}
\multicolumn{1}{c|}{Feature} & Value \\ \hline
\multicolumn{1}{c|}{Accuracy} & 0.972 \\ \hline
\multicolumn{1}{c|}{NIR} & 0.869 \\ \hline
\multicolumn{1}{c|}{$\phi$} & 0.8746\\ 
\label{DecisionTree_perf_tab}
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\caption{Performances of random forest algorithm for the exoplanets habitability as evaluated by the accuracy, the no-information rate (NIR), and the $\phi$ factor.}
\begin{center}
\begin{tabular}{l|l}
\multicolumn{1}{c|}{Feature} & Value \\ \hline
\multicolumn{1}{c|}{Accuracy} & 0.964 \\ \hline
\multicolumn{1}{c|}{NIR} & 0.869 \\ \hline
\multicolumn{1}{c|}{$\phi$} & 0.835 \\ 
\label{Random Forest_perf_tab}
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[htp]
  \centering
\subfloat[]{\label{Decision_Tree_FINAL_CV}\includegraphics[width=0.6\textwidth]{Pic/Decision_Tree_FINAL_CV.pdf}}\\
\subfloat[]{\label{Decision_Tree_FINAL_CV}\includegraphics[width=0.6\textwidth]{Pic/Decision_Tree_FINAL_ROC.pdf}}
\caption{The performances of the decision tree algorithm on the habitability of exoplanets as given by the confusion matrix (upper panel) and ROC curve (lower panel) as obtained by a 10-fold cross validation. A predicted (P) habitable exoplanet is classified as \textit{True} while a test (T) non-habitable exoplanet is classified as \textit{False}}
\label{Decision_tree_performances}
\end{figure}
